MINOS Handover Plots

### 2023-07-06 minos/validation/handovers.Rmd
Fixed some references to SF_12 -> SF_12_MCS, and fixed the PCS section also

```{r, warning=FALSE}
raw.inc <- raw.dat %>%
  select(pidp, age, time, hh_income)
base.inc <- base.dat %>%
  select(pidp, age, time, hh_income)

@@

## SF12

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.sf12 <- raw.dat %>% 
  dplyr::select(pidp, time, SF_12) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12 <- base.dat %>%
  dplyr::select(pidp, time, SF_12) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
sf12 <- rbind(raw.sf12, base.sf12)

# Now plot
ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('SF12')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.sf12.2 <- raw.dat %>% 
  dplyr::select(pidp, time, SF_12) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.2 <- base.dat %>%
  dplyr::select(pidp, time, SF_12) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

sf12.2 <- rbind(raw.sf12.2, base.sf12.2)

# Now plot
ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Mental Wellbeing (SF12 MCS)') +
  xlab('Year') +
  ylab('SF12')

if (shall.we.save) {
  ggsave(filename = 'SF12_wav1.png',
       plot = last_plot(),
       path = save.path)
}

@@

```{r}
raw.sf12 <- raw.dat %>%
  select(pidp, age, time, SF_12)
base.sf12 <- base.dat %>%
  select(pidp, age, time, SF_12)

sf12.spag <- rbind(raw.sf12, base.sf12)

spaghetti_plot(sf12.spag, 'SF_12',
               save = shall.we.save,
               save.path = save.path)

rm(raw.sf12, base.sf12, sf12.spag)
```

@@

```{r, warning=FALSE}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'education_state')

>>>>

```{r}
raw.inc <- raw.dat %>%
  select(pidp, age, time, hh_income)
base.inc <- base.dat %>%
  select(pidp, age, time, hh_income)

@@

## SF_12_MCS

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.sf12.m <- raw.dat %>% 
  dplyr::select(pidp, time, SF_12_MCS) %>%
  filter(SF_12_MCS > 0) %>%
  group_by(time) %>%
  summarise(sf12.m = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.m <- base.dat %>%
  dplyr::select(pidp, time, SF_12_MCS) %>%
  filter(SF_12_MCS > 0) %>%
  group_by(time) %>%
  summarise(sf12.m = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
sf12.m <- rbind(raw.sf12.m, base.sf12.m)

print(sum(sf12.m$SF_12_MCS < 0))

# Now plot
ggplot(data = sf12.m, mapping = aes(x = time, y = sf12.m, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Mental Wellbeing (SF12_MCS)', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('SF12_MCS')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.sf12.m.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.sf12.m.2 <- raw.dat %>% 
  dplyr::select(pidp, time, SF_12_MCS) %>%
  filter(SF_12_MCS > 0) %>%
  filter(pidp %in% raw.sf12.m.wave1) %>%
  group_by(time) %>%
  summarise(sf12.m = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.m.2 <- base.dat %>%
  dplyr::select(pidp, time, SF_12_MCS) %>%
  filter(SF_12_MCS > 0) %>%
  filter(pidp %in% raw.sf12.m.wave1) %>%
  group_by(time) %>%
  summarise(sf12.m = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

sf12.m.2 <- rbind(raw.sf12.m.2, base.sf12.m.2)

# Now plot
ggplot(data = sf12.m.2, mapping = aes(x = time, y = sf12.m, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Mental Wellbeing (SF12_MCS)') +
  xlab('Year') +
  ylab('SF12_MCS')

if (shall.we.save) {
  ggsave(filename = 'SF12_MCS_wav1.png',
       plot = last_plot(),
       path = save.path)
}

@@

```{r}
raw.sf12.m <- raw.dat %>%
  select(pidp, age, time, SF_12_MCS)
base.sf12.m <- base.dat %>%
  select(pidp, age, time, SF_12_MCS)

sf12.m.spag <- rbind(raw.sf12.m, base.sf12.m)

spaghetti_plot(sf12.m.spag, 'SF_12_MCS',
               save = shall.we.save,
               save.path = save.path)

rm(raw.sf12.m, base.sf12.m, sf12.m.spag)
```

## SF_12_PCS

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.sf12.p <- raw.dat %>% 
  dplyr::select(pidp, time, SF_12_PCS) %>%
  filter(SF_12_PCS > 0) %>%
  group_by(time) %>%
  summarise(sf12.p = mean(SF_12_PCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.p <- base.dat %>%
  dplyr::select(pidp, time, SF_12_PCS) %>%
  filter(SF_12_PCS > 0) %>%
  group_by(time) %>%
  summarise(sf12.p = mean(SF_12_PCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
sf12.p <- rbind(raw.sf12.p, base.sf12.p)

# Now plot
ggplot(data = sf12.p, mapping = aes(x = time, y = sf12.p, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Physical Wellbeing (SF12_PCS)', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('SF12_PCS')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.sf12.p.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.sf12.p.2 <- raw.dat %>% 
  dplyr::select(pidp, time, SF_12_PCS) %>%
  filter(SF_12_PCS > 0) %>%
  filter(pidp %in% raw.sf12.p.wave1) %>%
  group_by(time) %>%
  summarise(sf12.p = mean(SF_12_PCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.p.2 <- base.dat %>%
  dplyr::select(pidp, time, SF_12_PCS) %>%
  filter(SF_12_PCS > 0) %>%
  filter(pidp %in% raw.sf12.p.wave1) %>%
  group_by(time) %>%
  summarise(sf12.p = mean(SF_12_PCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

sf12.p.2 <- rbind(raw.sf12.p.2, base.sf12.p.2)

# Now plot
ggplot(data = sf12.p.2, mapping = aes(x = time, y = sf12.p, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Physical Wellbeing (SF12_PCS)') +
  xlab('Year') +
  ylab('SF12_PCS')

ggsave(filename = 'SF12_PCS_wav1.png',
       plot = last_plot(),
       path = save.path)
```

```{r}
raw.sf12.p <- raw.dat %>%
  select(pidp, age, time, SF_12_PCS)
base.sf12.p <- base.dat %>%
  select(pidp, age, time, SF_12_PCS)

sf12.p.spag <- rbind(raw.sf12.p, base.sf12.p)

spaghetti_plot(sf12.m.spag, 'SF_12_PCS',
               save = shall.we.save,
               save.path = save.path)

rm(raw.sf12.p, base.sf12.p, sf12.p.spag)
```

@@

```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'education_state')
